\ch{RELIKE}: Reionization Effective Likelihood from Planck 2018 Data (?)

### 2021-03-30 paper/rei.tex

\ch{Our code is available on GitHub at \url{...} [give URL]. } The initial release corresponds to the fiducial results in this paper, i.e.\ derived from the Planck 2018 $\texttt{plik\_lite\_TTTTTE} + \texttt{lowl} + \texttt{SRoll2}$ likelihoods at $\zmax = 30$. 
The most important part of the code release is the python package called \texttt{Relike} which \wh{provides the PC parameters for a model and also} 
% added this since it now seemed to be emphasizing Gaussian only  - not sure that was intentional.
implements the Gaussian effective likelihood. The user can specify a customized $x_e(z)$ function taking in reionization model parameters and use \textt{Relike} to return the effective likelihood of the model. The returned likelihood is already marginalized over cosmological parameters. 
To obtain marginalized distributions more easily for high-dimensional parameter space, one may choose to sample \texttt{Relike} within a MCMC sampler such as Cobaya or Cosmosis \ch{[cite]}.

@@

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Cumulative optical depth in the tanh model as in Fig.~\ref{fig:tanh}
(68\% and 95\% C.L. contours).  Overall agreement is good in regions where the contribution to $\tau_{\rm tanh}$ is high but the model form forbids high-$z$ contributions.   The KDE and Gaussian PC results  oscillate around zero at high-z because of effective low pass filter of the truncation to 5 PCs (enough to represent any observable effects in the data).  \wh{maybe $\tau_{\rm tanh}$} }
%double check plot, upper and lower limits seem to cross?
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}

>>>>

Our code is available on GitHub at \todo{give URL\url{...}}. The initial release corresponds to the fiducial results in this paper, i.e.\ derived from the Planck 2018 $\texttt{plik\_lite\_TTTTTE} + \texttt{lowl} + \texttt{SRoll2}$ likelihoods at $\zmax = 30$. 
The most important part of the code release is the python package called RELIKE which \wh{provides the PC parameters for a model and also} 
% added this since it now seemed to be emphasizing Gaussian only  - not sure that was intentional.
implements the Gaussian effective likelihood. The user can specify a customized $x_e(z)$ function taking in reionization model parameters and use \textt{Relike} to return the effective likelihood of the model. The returned likelihood is already marginalized over cosmological parameters. 
To obtain marginalized distributions more easily for high-dimensional parameter space, one may choose to sample RELIKE within a MCMC sampler such as Cobaya or Cosmosis \ch{[cite]}.

@@

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_tanh_direct_vs_kde_vs_gaussian.pdf}
\caption{Cumulative optical depth in the tanh model as in Fig.~\ref{fig:tanh}
(68\% and 95\% C.L. contours).  Overall agreement is good in regions where the contribution to $\tau_{\rm tanh}$ is high but the model form forbids high-$z$ contributions.   The KDE and Gaussian PC results  oscillate around zero at high-z because of effective low pass filter of the truncation to 5 PCs (enough to represent any observable effects in the data). }
\label{fig:plot_taugtz_PC_vs_tanh}
\end{figure}
